Lichat, A Lightweight Chat Protocol

### 2022-01-25 els2022-lichat/paper.tex
Minor

@@

>>>>

Another topic of interest is the implementation of a full bridge for the Matrix protocol, which would allow Lichat servers to interact with the Matrix federated ecosystem.

@@

Finally we would like to extend the existing clients to support all of the drafted extensions, and further improve the Elixir server to support statistics gathering and allow for better spam and abuse control.
